---
title: "linear model from Web"
author: "Hayden Wood"
date: "Spring 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```
## Introduction     

we will produce 3 equation models to get       
1. Sim score base on arm strength        
2. Sim score based on grip        
3. Sim score based on both arm and grip strength         

for each model we will predict sim for arm=88, grip=94

## Methods

We have numerical responses (sim score) and numerical explanatory variables which are ( arm and grip strength)         
so we use Numerical~Numerical helper file

## Model 1 SIM~ARMS

## Results   

### scatterplot

```{r}
plot(GRIP~ARM,data=data)
```

There is a positive relatonship between SIMS and ARMS. If this was a perfect linear all the plots would be on a straight line. The corrleation between Arm strength and Sims are .0         
          
### Numerical results


### Inferential  (Build model.1)

#### Predict at target point


#### scatterplot with model fit
  

## Model 2 SIM~GRIP

### Now add in scatterplot


### Numerical results 


### Inferential  (Build model.2)
  

#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

`
  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

